``EGGs are adhesive!''\\ Answer to reviewers

### 2025-05-18 calco/rebuttal/letter.tex
passata

\documentclass[english,11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{amsfonts}
\usepackage{cleveref}
\usepackage{fullpage}

@@

ANSWER: there is a pointer to the appenix befor Lemma 2.12. Such pointer (and all the others) are there to provide the reader with a quick link to the correct proof in the appendix.

@@

ANSWER: In Prop.~2.13 it is not assumed that the bottom face is a pushout, eve if this property can be deduced from $\mathcal{M}$-adhesivity. Notice, however that to Prop.~2.13 it should be enough to ask for stability of $\mathcal{M}$-pushouts: in such a case the bottom face of the cube is not guaranteed to be a pushout (we do not need such level of generality here).

@@

ANSWER: we removed the brackets since they were useless. Since we are identifying $1^\star$ with $\mathbb{N}$, $\gamma_1$ as codomain $\mathbb{N}$is precisely the element $1\in \mathbb{N}$.

@@

 \item $214$: It seems to me that the second diagram can first be explained in much simpler terms, such as "in labelled hypergraphs, all hyperedges must have a single target vertex", and then it could be restated as a factorisation result for $t_\mathcal{H}$. The current explanation is not clear enough.

@@

 \item $215$: What is $U_{\mathbf{X}}$? Is it $U_{\mathbf{Set}}$? Or maybe $U_{\mathbf{Hyp}}$ that gives the set of vertices? There has been a lot of forgetful functor introduced so far, and here is one more being defined, so it would help to have a description in words added to this sentence.

@@

\item $224-225$: What do you mean by "identifier"? Do you mean "label"? And what does "the latter" refer to?

ANSWER: changed with "labels"

@@

ANSWER: added

@@

ANSWER: That's true but it seems to us that this formulation is neither clearer nor more informative that ours.

@@

ANSWER: if $1$ has no hyperedge than no argument is needed since $\mathcal{G}_a$ does not have arrows into it. If $1$ has one hyperedge than the existence of arrows $\mathcal{G}_a\to 1$ and $\mathcal{G}_b\to 1$ entails that $a=b$, which is a contradiction. Alll the details are in the cited reference [10].

\item $259$: The wording is confused: "then its pushout along (f2,g2), then their pushout".

@@

\item $263$: How does Corollary 3.27 follow from Proposition 2.4, Proposition 3.25, and Lemmma 3.26? This needs to be fleshed out. Does it use the fact that $\mathbf{Hyp}$ is adhesive (Corollary 3.6) and the subcategory property of Proposition 2.4?

@@

\item $273$: Why is the notation $h_C$ and not $h_Q$?
ANSWER: Fixed.

\item $285$: Do you mean to say that proofs (pural) of Section 4 can be found in Appendix A.2?

ANSWER: This pointer refers to the proof of Prop.~4.4. There is another pointer some lines below for the proof of Lem,~4.8.

@@

ANSWER: in our opinion it would not enhance the clarity of the paper.

@@

ANSWER: we do not find the original sentence confusing at all. We nonetheless rephrased it.

@@

\item $307$: Be more precise about the sense in which you mean ``suitable", i.e., as the suitable class of monos $\mathcal{M}$ for which $\mathcal{M}$-adhesivity holds.

ANSWER: we find the meaning completely clear from the context. Moreover, the meaning of ``suitable'' is made explicit by the content of Lem.~4.11.

@@

\item $325$: You could mention that $EqHyp_\Sigma$ can be seen as the comma category $T \downarrow$ ``Constant functor at $\mathcal{G}^\Sigma$". This would make the parallel with the definition of the category of labelled hypergraphs that was defined as a slice category. Moreover, you could then give a reference for the proof of Proposition 4.17, such as [MacLane Categories for the working mathematician, IV.1, Exercise 2, p86].

ANSWER: We rather not: what the reviewer asked us to mention is exactly the content of Prop.~4.17. In turn, we do not see any need to quote the exercise of MacLane's book since the proof Prop.~4.17 it's a complete triviality.

\item $327$: ``to the arrow" -> ``to an arrow"? And why is this arrow necessarily of the form (l,!)? Please provide more details

ANSWER:  no: as mentioned, $R$  is the right adjoint to $T$ so $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to a unique arrow $\mathcal{H}\to R(\mathcal{G}_\Sigma)$. That this mate is exactly $(l, !_{V_{\mathcal{H}}})$ follows from the proof of Prop.~4.4 but it's also commpletely obvious given the definition of $\mathcal{G}^\Sigma$.

@@

ANSWER: we do not think that these details should be provided because they are already contained in the  Proposition, Lemma and Corollaries quoted.  added a reference to Cor.~B.11 in which the details are spelled out even more explicitly.  Point $1$ follows immediately from Cor.~B.11 and Lem.~4.8 and point $2$ is simply the closure of adhesivity properties under the slice construction.

@@

ANSWER: we do not think that there is a need to provide an explicit example. If the reviewer needs one, it can equip the term graph of Ex.~3.21 with the equality

\item $344$: ``Thus ... right": You meant to say that $S_\Sigma$ makes the diagram on the right commute, right? Moreover, please describe what $S_\Sigma$ does explicitly, and why it would make the diagram commute.

ANSWER: the action of $S_\Sigma$ is already in the text: it sends $(\mathcal{H},l)$ to $(T(\mathcal{H}),l)$.

\item $345$: Please provide a proof of this claim.
ANSWER: we have already provided the proof citing Cor.~4.5 and Prop.~4.18.

@@

ANSWER: we added a reference to Cor.~4.19  and we believe that this is all that's needed.

@@

ANSWER: we do not think that a further explanation is needed because the equation $q^\star \circ t\circ \pi_1= q^\star \circ t \circ \pi_2$ is \emph{exactly} the symbolic translation of ``whenever the relation identifies the source of two hyperedges, it identifies their targets too''.

@@

ANSWER: this would be unnecessary and space consuming.

\item $368$: Why does going from ``hypergraph with equivalence" to ``e-hypergraph" result in the category names going ``EqHyp" to ``GEqHyp"? What does the ``G" mean?

ANSWER: notation changed to $\mathsf{e}-\mathbf{EqHyp}$

\item $369-370$: Please add an example of an e-hypergraph.
ANSWER: added an example

\item $374$: "is so" -> "is a regular mono"

@@

\item $383$: Does the use of the word ``context" in this sentence refer to its common meaning in graph rewriting?

ANSWER: no.

ANSWER: no, see the answers above about the isomorphism between $\mathbb{N}$ and $1^\star$.

\item $405$: Why the name ``EGG"? Why is this short for ``e-term graph"?

ANSWER: indeed the name ``EGG'', which comes from the already existing literature, is short for ``e-term graph'' or for ``e-graph''.

ANSWER: we disagree on the fact that such an explanation is necessary: it is simply the restriction of $\mathcal{T}$ to the subcategory $\mathbf{EGG}$ and $\mathcal{T}$ has been already descripted in elementary terms.

TO DO
\item $442$: What is ``their nature"?

TO DO
\item $443-444$: what do you mean by ``the drawback ... same rewriting step"?

ANSWER: we disagree with the reviewer and we think that all the details needed for the proof to be followed have been provided.

\item $581$: here and also at multiple other places, the word ``thesis" is used in a way I haven't heard yet. Please check if this is a correct meaning of the word or replace it with something more appropriate like ``claim" or ``statement".

\item $581-582$: ``two rectangles below are pullbacks" Explain why in more details: left square is a pullback by definition of kernel pairs, and right square is a pullback by assumption, thus by Lemma A1 the outer square is also a pullback.

ANSWER: all the details cited by the reviewer are already in the text (they are quite literally the hypotheses of Lem.~2.12) and so we do not find necesary to recall them again in the proof.

ANSWER: we think that such diagram is not needed and a waste of space.

ANSWER: we didn't find a more abstract proof, even if we suspect that the present proof works in any extensive and distributive monoidal category (see the answer above regarding the Kleene star).

ANSWER: in line $600$ we are using the universal property of a product to \emph{define} the arrow $\phi$, so we do not understand the reviewer's question. Adding a diagram here would be completely uninformative.

ANSWER : fixed.

ANSWER: fixed. No, the uniqueness invoked in line $602$ is not the same that we must be proved: we know that $\psi$ is the unique arrow such that $\psi \circ n=k$ and $\psi \circ h =\phi$. A further (even if elementary) step is needed to show that it is the unque arrow such that it is the unique one such that $\psi \circ n=k$ and $\psi \circ h \circ \iota_m=f$. Notice that the uniqueness cited in line $602$ is used in the last line to conclude the proof.

\item $607$: Say that the first claim is by monotonicity of $m$.
ANSWER: fixed.

\item $607$: Why does $(B,{m,\iota_m})$ being a coproduct implies that $\psi' = \psi$? Explain more

ANSWER: this is an error which we have fixed. What we are using here is that $(D, \{n, h\})$ is a pushout.

@@

ANSWER: we prefer our formulation.

\item $631$: ``By Lemma A.2 … coproduct." Draw the diagram or mention explicitly which pushout square we consider (i.e., the one on top)

ANSWER: there is no need to draw a diagram since we already mention that we are referring to $(D', \{n', g'\circ \iota\})$ and there is only one pushout in which $D'$ appears.

@@

ANSWER: this change, which amounts to a rotation of the cube, has been done for typographical reason and it is completely harmful.

\item $631$: Put the sentence ``We can … the right" in the same paragraph as its explanation.

@@

ANSWER: we prefer the actual formulation.

\item $632$: ``the dotted arrow": mention its name

\item $633$: Draw the corresponding diagram

ANSWER: there is no need to do so and it would be simply a waste of space.

@@

ANSWER: we find this sentence clear as it is.

\item $638$: Draw the corresponding diagram

ANSWER: as in many previous answers, such diagram is not needed since the two equations are as informative as that.

@@

ANSWER: indeed we are using that propery, which hold by the observations before the bullet points. As in the answers before, we do not think that repeating all the hypotheses used every half of a page is needed.

\item $643-644$ Mention more explicitly what "the thesis" is in order to guide the reader and make a stronger case for you proof. You're trying to prove the square $B'D'BD$ is a pullback, i.e., to show there exists a unique morphism/function $k \colon  T \to B'$ such that $b\circ k=t_2$ and $n'\circ k = t_1$. For the existence of such a $k$, mention explicitly that $h_1 \circ l_1^{-1}$ is one such morphism that satisfies the two desired equalities. For the uniqueness of $k$, detail more why it follows from $n'$ being a mono.

ANSWER:  we do not believe that such additional observations are needed, especially if they amounts to restating that we are trying to prove the universal property of pullbacks! Similarly, it's a completely trivial observation that then monotonicity of $n'$ entails uniqueness.

@@

ANSWER: we agree that this result is very technical and its proof quite involved. That's why it's been deferred to the appendix. However, as in the answer above we do not find the need to restate our claims. We also find the strategy quite natural and a standard application of extensivity and distributivty.

@@

ANSWER: we prefer to maintain the current formulation.

@@

ANSWER: we've added a reference to Lem.~A.2

@@

ANSWER: $j_0$ \emph{is} $k_{n'}$, compare the third rectangle of Lem.~2.12. That's why there is a pointer to such lemma.

@@

ANSWER: this approach would occupy much more space and, in our opinion, not add much in terms of clarity. The equation mentioned by the reviewer follows from the definition of kernel pair.

\item $645-705$: The rest of the proof is difficult to follow and could benefit from restructuring and more guiding. What is the prupose of seeing $K_d$ and $K_3$ as coproducts? For $K_d$, this is used on lines $697-698$, but I don't see a similar use for $K_3$ (maybe it's my bad).

ANSWER: we did not decompose $K_3$ as a coproduct. Lines $659-666$ are needed to build $\phi_3$, which is used later. As pointed out by the reviewer, the decomposition of $K_d$ is used in lines $697-698$.

\item $715-716$: Please flesh out this last sentence finishing the proof in more details, and provide appopropriate diagrams.

ANSWER: as in some answers above, we do not find useful to draw the diagram alongide the equation.

\item $719-722$: Same comment

ANSWER: same as above.

@@

ANSWER: same as above. It is a very well known fact that a natural transformation between two diagrams induces an arrow between the colimits and there is no need to restate it.

@@

ANSWER: they are \emph{defined} as coprojojections, so there is no need to further specify their typings.

@@

\item $737$: ``By Lemma B.3 ...": The use of this lemma is too quick, with important details missing. Which comma category are you considering? The only one considered so far is $\mathbf{Hyp} = \mathsf{id}_{\mathbf{Set}} \downarrow \mathsf{prod}^\star$. If that's the case, which functor are you considering to play the role of $F$ in Lemma B.3? Is it $T\circ F : \mathbf{D} \to  \mathbf{Hyp}$? The conclusion of your sentence is about the colimit of $U_{\mathsf{eq}}\circ F$, which has type $\mathbf{D} \to \mathbf{EqHyp} \to \mathbf{Set}$, so are you instead considering $\mathbf{Set}$ as a (trivial) comma category? If you want to invoke Lemma B.3, you also need to prove that the functor $L$ preserves colimits along $U_L \circ F$, which you don't mention.

ANSWER: We beg to disagree that the use of this lemma is too quick. The further comments of the reviewer suggest that some misunderstanding is at play here. Indeed we are considering the fact that $\mathbf{Hyp}$ is equivalent to $\mathsf{id}_{\mathbf{Set}} \downarrow \mathsf{prod}^\star$. By Lem.~B.3 $\{U_L, U_R\}$ jointly creates colimits of $F$, in particular $U_L$ preserves colimits and so $(V, \{\kappa^D_V\})$ is colimiting as claimed. Notice that, In our case $L$  is the identity and so it preserves colimits along any $F$, moreover $U_L$ becomes $U_{\mathsf{eq}}$.

@@

ANSWER: see answers above: we do not find necessary to draw diagrams here.

\item $742$: ``by construction": Difficult to see without diagrams/equations/etc.

ANSER: see above.

@@

ANSWER: we believe that such summary is neither needed nor informative.

@@

ANSWER:  see answers above: we do not think that adding such diagram is useful.

\item $753$: ``We know ...": it seems you're doing a (regular epi,mono) factorisation of $l$. If that's the case, please be explicit about it.

ANSWER: indeed we are doing such a factorization. We have out a reference to Rem.~A.6

\item $753$: ``Since the identity ...": it seems you're using the property of q being a regular epi. If that's the case, please be explicit about it (and give a reference to Remark A.6)

ANSWER: added.

@@

ANSWER: we prefer our original formulation.

@@

ANSWER: We have sistematically avoided the use the tail for isos as the identities. Moreover adding the tail here is completely not informative.

@@

ANSWER: this is just an application of faithfullness of $T$. Added.

\item $763$: ``Hence": You're using the uniqueness of the function $V_G \to L$ in the universal property of L as the limit of KF. Please be explicit about it.

@@

ANSWER:  We are applying Cor.~B.4 to the category of hypergraphs. Since the Kleene stars preserves connected limits then, in particular, equalizers are computed componentwise (another proof is obtained appealing to the presentation of term graphs as presheaves).

@@

ANSWER: we do not think that it should be mentioned explicitly that the composit of two monos is mono.

\item $769$: What are the ``witnesses"? You're trying to prove that $(h_E,H_V,h_Q)$ is a regular mono. Be more precise.

ANSWER: rephrased.

@@

ANSWER: this appendix is entirely technical and contains only very well known results. As such it has been quoted only when needed.

\item $911$: What is the reference [9,10] for? For the statement or proof of Lemma B.3? For the definition of what "jointly creating colimits" means?

@@

\item $911$: Can you give a detailed explanation or example of what you mean by ``$\{U_L, U_R\}$ jointly creates colimits of $F$"? The definition is currently diluted in the proof, and the reader could benefit greatly from having it from the get-go.

ANSWER: see the answers above. Since this is a technical appendix we think that it sufficient to provide a pointer to the relevant literature.

\item $914$: The word ``define" does not really fit, as F is already defined. Maybe "denote"?

@@

ANSWER: since this result is entriely known and elementary, we do not think that drawing a diagram is necessary.

@@

ANSWER: same answer as above.

\item $921$: Shouldn't it be $(L(a_D'),R(b_D'))$ everytime? Also, shouldn't $F(d) = (LU_LF(d),RU_RF(d))$?

ANSWER:  no, it's correct in this formulation.

@@

ANSWER: same answers regardin the diagrams as above.

@@

ANSWER: same answer as above.

\item $932$: What is the functor I? Is this a typo for F?
ANSWER: Indeed, fixed.

@@

ANSWER: a category can have more than one terminal/inital objects, albeit if they are, obviously, all isomorphic.

\item $948$: The argument for the uniqueness of $(?_A,k)$ could be made clearer. A diagram of the universal morphism would have been helpful

ANSWER: fixed a typo. We do not think that a further clarification is needed.

@@

	ANSWER: we do not believe that citing the suggested works would be helpful or appropriate, as they appear to be unrelated to the topic at hand.

@@

	ANSWER: indeed, fixed.

@@

	ANSWER: added a pointer to the relevant results.

@@

	ANSWER: added a pointer to the relevant results. We added in appendix the proof of the second point for which, while well known, we were unable to find a source in the literature (likely because it follows at once from the first point).

@@

ANSWER: this is a basic and elementary result of basic category theory.

@@

ANSWER: the only not obvious property of the Kleene star is the first and the reference is provided.

@@

	\item  $438$: "introductory example in [32]" -> give example number if it exists, or section/page number.

@@

ANSWER: added the reference.

@@

	ANSWER: this is a well known fact and so we believe that no further reference is needed.

@@

	ANSWER: added the relevant references.

@@

	ANSWER: this is an exercise using the definition of distributivity and extensivity.

@@

ANSWER: preservation of pullbacks always entails preservation of monos. This is again an exercise in basic category theory.

@@

	ANSWER: see answer above.

@@

ANSWER: see above.

@@

ANSWER: we do not believe that there is the need to recall the definition of continuity nor that limits commute with limits.

@@

	ANSWER: added references.

@@

	ANSWER: this is, again, an easy exercise of basic category theory.

@@

\item $111$: category L -> category, L
ANSWER: fixed.

>>>>

\documentclass[english,11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{amsfonts}
\usepackage{cleveref}
\usepackage{fullpage}
\usepackage{xcolor}

@@

ANSWER: there is a pointer to the appendix before Lemma 2.12. Such pointer (and all the others) are there to provide the reader with a quick link to the correct proof in the appendix.

@@

ANSWER: In Prop.~2.13 it is not assumed that the bottom face is a pushout, even if this property can be deduced from $\mathcal{M}$-adhesivity. Notice however that to Prop.~2.13 it should be enough to ask for stability of $\mathcal{M}$-pushouts: in such a case the bottom face of the cube is not guaranteed to be a pushout (we do not need such level of generality here).

@@

ANSWER: we removed the brackets since they were useless. Since we are identifying $1^\star$ with $\mathbb{N}$, $\gamma_1$ as codomain $\mathbb{N}$ is precisely the element $1\in \mathbb{N}$.

@@

 \item $214$: It seems to me that the second diagram can first be explained in much simpler terms, such as ``in labelled hypergraphs, all hyperedges must have a single target vertex'', and then it could be restated as a factorisation result for $t_\mathcal{H}$. The current explanation is not clear enough.

@@

 \item $215$: What is $U_{\mathbf{X}}$? Is it $U_{\mathbf{Set}}$? Or maybe $U_{\mathbf{Hyp}}$ that gives the set of vertices? There has been a lot of forgetful functors introduced so far, and here is one more being defined, so it would help to have a description in words added to this sentence.

@@

\item $224-225$: What do you mean by ``identifier''? Do you mean ``label'' And what does ``the latter'' refer to?

ANSWER: Changed with ``labels''.

@@

@@

ANSWER: That is true but it seems to us that this formulation is neither clearer nor more informative that ours.

@@

ANSWER: If $1$ has no hyperedge than no argument is needed since $\mathcal{G}_a$ does not have arrows into it. If $1$ has one hyperedge than the existence of arrows $\mathcal{G}_a\to 1$ and $\mathcal{G}_b\to 1$ entails that $a=b$, which is a contradiction. All the details are in the cited reference [10].

\item $259$: The wording is confused: ``then its pushout along (f2,g2), then their pushout''.

@@

\item $263$: How does Corollary 3.27 follow from Proposition 2.4, Proposition 3.25, and Lemma 3.26? This needs to be fleshed out. Does it use the fact that $\mathbf{Hyp}$ is adhesive (Corollary 3.6) and the subcategory property of Proposition 2.4?

@@

\item $273$: Why is the notation $h_C$ and not $h_Q$?

\item $285$: Do you mean to say that proofs (plural) of Section 4 can be found in Appendix A.2?

ANSWER: This pointer refers to the proof of Prop.~4.4. There is another pointer some lines below for the proof of Lem.~4.8.

@@

ANSWER: We believe it would not enhance the clarity of the paper.

@@

ANSWER: We do not find the original sentence confusing. We nonetheless rephrased it.

@@

\item $307$: Be more precise about the sense in which you mean ``suitable'', i.e., as the suitable class of monos $\mathcal{M}$ for which $\mathcal{M}$-adhesivity holds.

ANSWER: We find the meaning  clear from the context. Moreover, the meaning of ``suitable'' is made explicit by the content of Lem.~4.11.

@@

\item $325$: You could mention that $EqHyp_\Sigma$ can be seen as the comma category $T \downarrow$ ``Constant functor at $\mathcal{G}^\Sigma$''. This would make the parallel with the definition of the category of labelled hypergraphs that was defined as a slice category. Moreover, you could then give a reference for the proof of Proposition 4.17, such as [MacLane Categories for the working mathematician, IV.1, Exercise 2, p86].

ANSWER: We rather not: what the reviewer asked us to mention is exactly the content of Prop.~4.17. In turn, we do not see any need to quote the exercise of MacLane's book since the proof Prop.~4.17 is trivial.

\item $327$: ``to the arrow'' -> ``to an arrow''? And why is this arrow necessarily of the form (l,!)? Please provide more details

ANSWER:  No: as mentioned, $R$  is the right adjoint to $T$ so $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to a unique arrow $\mathcal{H}\to R(\mathcal{G}_\Sigma)$. That this mate is exactly $(l, !_{V_{\mathcal{H}}})$ follows from the proof of Prop.~4.4 but it is also obvious given the definition of $\mathcal{G}^\Sigma$.

@@

ANSWER: We do not think that these details should be provided because they are already contained in the  Proposition, Lemma and Corollaries quoted. We added a reference to Cor.~B.11 in which the details are spelled out even more explicitly.  Point $1$ follows immediately from Cor.~B.11 and Lem.~4.8 and point $2$ is simply the closure of adhesivity properties under the slice construction.

@@

ANSWER: We believe that there is no need to provide an explicit example. %If the reviewer needs one, it can equip the term graph of Ex.~3.21 with the equality

\item $344$: ``Thus ... right'': You meant to say that $S_\Sigma$ makes the diagram on the right commute, right? Moreover, please describe what $S_\Sigma$ does explicitly, and why it would make the diagram commute.

ANSWER: The action of $S_\Sigma$ is already in the text: it sends $(\mathcal{H},l)$ to $(T(\mathcal{H}),l)$.

\item $345$: Please provide a proof of this claim.

ANSWER: We have already provided the proof citing Cor.~4.5 and Prop.~4.18.

@@

ANSWER: We added a reference to Cor.~4.19  and we believe that this is all that is needed.

@@

ANSWER: We believe that no further explanation is needed because the equation $q^\star \circ t\circ \pi_1= q^\star \circ t \circ \pi_2$ is \emph{exactly} the symbolic translation of ``whenever the relation identifies the source of two hyperedges, it identifies their targets too''.

@@

${\mathbf ANSWER: This would be unnecessary and space consuming.}$

\item $368$: Why does going from ``hypergraph with equivalence'' to ``e-hypergraph'' result in the category names going ``EqHyp'' to ``GEqHyp''? What does the ``G'' mean?

ANSWER: Notation changed to $\mathsf{e}-\mathbf{EqHyp}$

\item $369-370$: Please add an example of an e-hypergraph.

\item $374$: ``is so'' -> ``is a regular mono''.

\item $383$: Does the use of the word ``context'' in this sentence refer to its common meaning in graph rewriting?

ANSWER: No.

ANSWER: No, see the answers above about the isomorphism between $\mathbb{N}$ and $1^\star$.

\item $405$: Why the name ``EGG''? Why is this short for ``e-term graph''?

ANSWER: Indeed the name ``EGG'', which comes from the already existing literature, is short for ``e-term graph'' or for ``e-graph''.

ANSWER: We disagree that such an explanation is necessary: it is simply the restriction of $\mathcal{T}$ to the subcategory $\mathbf{EGG}$ and $\mathcal{T}$ has been already descripted in elementary terms.

ANSWER: We streamlined and cleaned up the presentation, also adding details.

ANSWER: Added explanation.

ANSWER: Added explanation.

\item $442$: What is ``their nature"?

ANSWER: Added explanation.

\item $443-444$: what do you mean by ``the drawback ... same rewriting step"?

ANSWER: Rephrased sentence.

ANSWER: Not necessarily, But for the EGGs rule, it suffices to forbid that the same rule is applied twice. Rephrased sentence.

ANSWER: We meant rules with negative application conditions. Added.

ANSWER: Rephrased sentence.

ANSWER: We disagree with the reviewer and we think that all the details needed for the proof to be followed have been provided.

\item $581$: here and also at multiple other places, the word ``thesis'' is used in a way I haven't heard yet. Please check if this is a correct meaning of the word or replace it with something more appropriate like ``claim" or ``statement".

\item $581-582$: ``two rectangles below are pullbacks''. Explain why in more details: left square is a pullback by definition of kernel pairs, and right square is a pullback by assumption, thus by Lemma A1 the outer square is also a pullback.

ANSWER: All the details cited by the reviewer are already in the text (they are quite literally the hypotheses of Lem.~2.12) and so we do not find necesary to recall them again in the proof.

{\color{red} ANSWER: we think that such diagram is not needed and a waste of space.}

ANSWER: We did not find a more abstract proof, even if we suspect that the present proof works in any extensive and distributive monoidal category (see the answer above regarding the Kleene star).

ANSWER: In line $600$ we are using the universal property of a product to \emph{define} the arrow $\phi$, so we do not understand the reviewer's question. Adding a diagram here would be uninformative.

ANSWER : Fixed.

ANSWER: Fixed. No, the uniqueness invoked in line $602$ is not the same that we must be proved: we know that $\psi$ is the unique arrow such that $\psi \circ n=k$ and $\psi \circ h =\phi$. A further (even if elementary) step is needed to show that it is the unque arrow such that it is the unique one such that $\psi \circ n=k$ and $\psi \circ h \circ \iota_m=f$. Notice that the uniqueness cited in line $602$ is used in the last line to conclude the proof.

\item $607$: Say that the first claim is by monotonicity of $m$.

@@

\item $607$: Why does $(B,{m,\iota_m})$ being a coproduct implies that $\psi' = \psi$? Explain more.

ANSWER: This is an error which we have fixed. What we are using here is that $(D, \{n, h\})$ is a pushout.

@@

ANSWER: We prefer our formulation.

\item $631$: ``By Lemma A.2 … coproduct.'' Draw the diagram or mention explicitly which pushout square we consider (i.e., the one on top)

ANSWER: There is no need to draw a diagram since we already mention that we are referring to $(D', \{n', g'\circ \iota\})$ and there is only one pushout in which $D'$ appears.

@@

ANSWER: This change, which amounts to a rotation of the cube, has been done for typographical reason and it is completely harmful.

\item $631$: Put the sentence ``We can \ldots the right'' in the same paragraph as its explanation.

@@

ANSWER: We prefer the actual formulation.

\item $632$: ``the dotted arrow'': mention its name

\item $633$: Draw the corresponding diagram.

{\color{red} ANSWER: there is no need to do so and it would be simply a waste of space.}

@@

ANSWER: We prefer the current formulation.

\item $638$: Draw the corresponding diagram.

{\color{red} ANSWER: As in many previous answers, such diagram is not needed since the two equations are as informative as that.}

@@

ANSWER: Indeed we are using that property, which hold by the observations before the bullet points. As in the answers before, we do not think that repeating all the hypotheses used every half of a page is needed.

\item $643-644$ Mention more explicitly what ``the thesis'' is in order to guide the reader and make a stronger case for you proof. You're trying to prove the square $B'D'BD$ is a pullback, i.e., to show there exists a unique morphism/function $k \colon  T \to B'$ such that $b\circ k=t_2$ and $n'\circ k = t_1$. For the existence of such a $k$, mention explicitly that $h_1 \circ l_1^{-1}$ is one such morphism that satisfies the two desired equalities. For the uniqueness of $k$, detail more why it follows from $n'$ being a mono.

ANSWER:  We do not believe that such additional observations are needed, especially if they amounts to restating that we are trying to prove the universal property of pullbacks! Similarly, it is a trivial observation that the monotonicity of $n'$ entails uniqueness.

@@

ANSWER: We agree that this result is very technical and its proof quite involved. That is why it has been deferred to the appendix. However, as in the answer above we do not find the need to restate our claims. We also find the strategy quite natural and a standard application of extensivity and distributivty.

@@

ANSWER: We prefer to maintain the current formulation.

@@

ANSWER: We have added a reference to Lem.~A.2.

@@

ANSWER: $j_0$ \emph{is} $k_{n'}$, compare the third rectangle of Lem.~2.12. That is why there is a pointer to such lemma.

@@

ANSWER: This approach would occupy much more space and, in our opinion, not add much in terms of clarity. The equation mentioned by the reviewer follows from the definition of kernel pair.

\item $645-705$: The rest of the proof is difficult to follow and could benefit from restructuring and more guiding. What is the purpose of seeing $K_d$ and $K_3$ as coproducts? For $K_d$, this is used on lines $697-698$, but I don't see a similar use for $K_3$ (maybe it's my bad).

ANSWER: We did not decompose $K_3$ as a coproduct. Lines $659-666$ are needed to build $\phi_3$, which is used later. As pointed out by the reviewer, the decomposition of $K_d$ is used in lines $697-698$.

\item $715-716$: Please flesh out this last sentence finishing the proof in more details, and provide appropriate diagrams.

ANSWER: As in some answers above, we do not find useful to draw the diagram alongside the equation.

\item $719-722$: Same comment.

ANSWER: Same as above.

@@

ANSWER: Same as above. It is a very well known fact that a natural transformation between two diagrams induces an arrow between the colimits and there is no need to restate it.

@@

ANSWER: they are \emph{defined} as coprojections, so there is no need to further specify their typings.

@@

\item $737$: ``By Lemma B.3 ...'': The use of this lemma is too quick, with important details missing. Which comma category are you considering? The only one considered so far is $\mathbf{Hyp} = \mathsf{id}_{\mathbf{Set}} \downarrow \mathsf{prod}^\star$. If that's the case, which functor are you considering to play the role of $F$ in Lemma B.3? Is it $T\circ F : \mathbf{D} \to  \mathbf{Hyp}$? The conclusion of your sentence is about the colimit of $U_{\mathsf{eq}}\circ F$, which has type $\mathbf{D} \to \mathbf{EqHyp} \to \mathbf{Set}$, so are you instead considering $\mathbf{Set}$ as a (trivial) comma category? If you want to invoke Lemma B.3, you also need to prove that the functor $L$ preserves colimits along $U_L \circ F$, which you don't mention.

ANSWER: We beg to disagree that the use of this lemma is too quick. The further comments of the reviewer suggest that some misunderstanding is at play here. Indeed we are considering the fact that $\mathbf{Hyp}$ is equivalent to $\mathsf{id}_{\mathbf{Set}} \downarrow \mathsf{prod}^\star$. By Lem.~B.3 $\{U_L, U_R\}$ jointly creates colimits of $F$, in particular $U_L$ preserves colimits and so $(V, \{\kappa^D_V\})$ is colimiting as claimed. Notice that in our case $L$  is the identity and so it preserves colimits along any $F$, moreover $U_L$ becomes $U_{\mathsf{eq}}$.

@@

ANSWER: See answers above: we do not find necessary to draw diagrams here.

\item $742$: ``by construction'': Difficult to see without diagrams/equations/etc.

ANSER: See above.

@@

ANSWER: We believe that such summary is neither needed nor informative.

@@

ANSWER:  See answers above: we do not think that adding such diagram is useful.

\item $753$: ``We know ...'': it seems you're doing a (regular epi,mono) factorisation of $l$. If that's the case, please be explicit about it.

ANSWER: indeed we are doing such a factorization. We put a reference to Rem.~A.6

\item $753$: ``Since the identity ...'': it seems you're using the property of q being a regular epi. If that's the case, please be explicit about it (and give a reference to Remark A.6)

@@

ANSWER: We prefer our original formulation.

@@

ANSWER: We have avoided the use the tail for isos as the identities. Moreover adding the tail here is not informative.

@@

ANSWER: This is  an application of the faithfulness of $T$. Added.

\item $763$: ``Hence'': You're using the uniqueness of the function $V_G \to L$ in the universal property of L as the limit of KF. Please be explicit about it.

@@

ANSWER:  We are applying Cor.~B.4 to the category of hypergraphs. Since the Kleene stars preserves connected limits then, in particular, equalizers are computed component-wise (another proof is obtained appealing to the presentation of term graphs as presheaves).

@@

ANSWER: We do not think that it should be mentioned explicitly that the composition of two monos is mono.

\item $769$: What are the ``witnesses''? You're trying to prove that $(h_E,H_V,h_Q)$ is a regular mono. Be more precise.

ANSWER: Rephrased.

@@

ANSWER: This appendix is entirely technical and contains only very well known results. As such it has been quoted only when needed.

\item $911$: What is the reference [9,10] for? For the statement or proof of Lemma B.3? For the definition of what ``jointly creating colimits'' means?

@@

\item $911$: Can you give a detailed explanation or example of what you mean by ``$\{U_L, U_R\}$ jointly creates colimits of $F$''? The definition is currently diluted in the proof, and the reader could benefit greatly from having it from the get-go.

ANSWER: See the answers above. Since this is a technical appendix we think that it sufficient to provide a pointer to the relevant literature.

\item $914$: The word ``define'' does not really fit, as F is already defined. Maybe ``denote''?

@@

ANSWER: Since this result is known and elementary, we do not think that drawing a diagram is necessary.

@@

ANSWER: Same answer as above.

\item $921$: Shouldn't it be $(L(a_D'),R(b_D'))$ every time? Also, shouldn't $F(d) = (LU_LF(d),RU_RF(d))$?

ANSWER:  No, it is correct in this formulation.

@@

ANSWER: Same answers regarding the diagrams as above.

@@

ANSWER: Same answer as above.

\item $932$: What is the functor I? Is this a typo for F?

ANSWER: Indeed, fixed.

@@

ANSWER: A category can have more than one terminal/initial objects, albeit if they are, obviously, all isomorphic.

\item $948$: The argument for the uniqueness of $(?_A,k)$ could be made clearer. A diagram of the universal morphism would have been helpful.

ANSWER: Fixed a typo. We do not think that a further clarification is needed.

@@

	ANSWER: We do not believe that citing the suggested works would be helpful or appropriate, as they appear to be unrelated to the topic at hand.

@@

	ANSWER: Indeed, fixed.

@@

	ANSWER: Added a pointer to the relevant results.

@@

	ANSWER: Added a pointer to the relevant results. We added in appendix the proof of the second point for which, while well known, we were unable to find a source in the literature (likely because it follows at once from the first point).

@@

ANSWER: This is an elementary result of basic category theory.

@@

ANSWER: The only not obvious property of the Kleene star is the first and the reference is provided.

@@

	\item  $438$: ``introductory example in [32]'' -> give example number if it exists, or section/page number.

@@

ANSWER: Added the reference.

@@

	ANSWER: This is a well known fact and so we believe that no further reference is needed.

@@

	ANSWER: Added the relevant references.

@@

	ANSWER: This is an exercise using the definition of distributivity and extensivity.

@@

ANSWER: Preservation of pullbacks always entails preservation of monos. This is again an exercise in basic category theory.

@@

	ANSWER: See answer above.

@@

ANSWER: See above.

@@

ANSWER: We do not believe that there is the need to recall the definition of continuity nor that limits commute with limits.

@@

	ANSWER: Added references.

@@

	ANSWER: This is, again, an easy exercise of basic category theory.

@@

\item $111$: category L -> category, L
